A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-22 4_method.tex
explain domains early

\begin{figure}\centering
\setlength{\figwidth}{0.24\columnwidth}
\setlength{\figwidthTwo}{0.15\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{MAT}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{VD}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{ST}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Datastructure}\label{shape_decomposition_datastructure}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
}
\label{skeletonization_comparison}
\end{figure}

@@

>>>>

\begin{figure}\centering
\setlength{\figwidth}{0.19\columnwidth}
\setlength{\figwidthTwo}{0.3\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{Medial Axis}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{Voronoi Diagram}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Data structure}\label{shape_decomposition_datastructure}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
\caption{Polygon Domains}\label{shape_decomposition_domains}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
}
\label{skeletonization_comparison}
\end{figure}

@@

The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
Each polygon in the input shape acquires it's own domain.
The domains of hole polygons are touching the domains of the outer polygon.
See \cref{shape_decomposition_domains}.
